Data preparation

### 2024-02-01 procesamiento/01-prod_prep-micro.Rmd
up

```{r eval=FALSE, include=FALSE}
# knitr::knit(input = here::here("procesamiento/prod_prep.Rmd"));file.remove("prod_prep.md")
# knitr::knit(input = here::here("procesamiento/prod_prep-macro.Rmd"));file.remove("prod_prep-macro.md")
```

@@

# Total of known occupations
isei_ocupnames<- names(select(df1,busdriver:teacher))
df1$know_total <- rowSums(x = select(df1,isei_ocupnames),na.rm = T)
# summary(df1$know_total)
sjlabelled::set_label(df1$know_total) <- 'Total of known occupations'
```

@@

>>>>

```{r eval=FALSE, include=FALSE}
knitr::knit(input = here::here("procesamiento/01-prod_prep-micro.Rmd"));file.remove("01-prod_prep-micro.md")
knitr::knit(input = here::here("procesamiento/02-prod_prep-macro.Rmd"));file.remove("02-prod_prep-macro.md")
```

@@

# Total of known occupations
isei_ocupnames<- names(dplyr::select(df1,busdriver:teacher))
df1$know_total <- rowSums(x = dplyr::select(df1,isei_ocupnames),na.rm = T)
# summary(df1$know_total)
sjlabelled::set_label(df1$know_total) <- 'Total of known occupations'
```

@@

df1<- df1 %>% group_by(country) %>% mutate(sum_know_total=sum(know_total))

df1$know_total_weight <- df1$know_total/df1$sum_know_total
df1$homclass_wght <- (as.numeric(df1$ingroup/df1$know_total*df1$know_total_weight))*1000 #the 1000 is for scaling purposes

summary(df1$homclass_wght)

cor(df1[,c("homclass","homclass_wght","egal2")],use = "complete.obs")

hist.default(df1$homclass)
hist.default(df1$homclass_wght)
